### 2014-12-23 ms/ms.Rmd
Reduce word count in abstract
Max of 350 for Ecology.

**2. Abstract**: Understanding how plants are plant constructed -- i.e. how key size dimensions and the amount of mass invested in different tissues varies among individuals -- is essential for modeling plant growth, estimating carbon stocks, and mapping energy-fluxes in the terrestrial biosphere. Allocation patterns can differ through ontogeny, but also among coexisting species, and among species adapted to or grown in different environments. While a variety of models dealing with biomass allocation exist, we lack a synthetic understanding of the underlying processes. This is partly due to the lack of suitable datasets for validating and parameterising models. To that end, we present the Biomass And Allometry Database (BAAD) for woody plants. The BAAD contains `r sum(!is.na(data[,vars]))` measurements collected in `r length(unique(data$studyName))` different studies, from `r nrow(data)` individuals across `r length(unique(data$species))` species. Most of these data are associated with an existing publication, however, raw data files were rarely made public at time of publication. Thus the BAAD contains individual level data from different studies, transformed into standard units and variable names. The transformations were achieved using a common workflow for all raw data files. Other features which distinguish the BAAD are: i) measurements were for individual plants rather than stand averages; ii) individuals spanning a range of sizes were measured; iii) inclusion of plants from 0.01-100m in height; and iii) biomass was estimated directly, i.e. not indirectly via allometric equations (except in very large trees where biomass was estimated from detailed sub-sampling). We included both wild and artificially grown plants. The dataset contains the following size metrics: total leaf area; area of stem cross-section, including sapwood, heartwood, and bark; height of plant and crown base, crown area and surface area; and the dry mass of leaf, stem, branches, sapwood, heartwood, bark, coarse roots and fine root tissues. We also report other properties of individuals (age, leaf size, leaf mass per area, wood density, nitrogen content of leaves and wood), as well as information about the growing environment (location, light, experimental treatment, vegetation type) where available. It is our hope that making these data available will improve our ability to understand plant growth, ecosystem dynamics, and carbon cycling in the world's vegetation.

>>>>

**2. Abstract**: Understanding how plants are plant constructed -- i.e. how key size dimensions and the amount of mass invested in different tissues varies among individuals -- is essential for modeling plant growth, estimating carbon stocks, and mapping energy-fluxes in the terrestrial biosphere. Allocation patterns can differ through ontogeny, but also among coexisting species, and among species adapted to different environments. While a variety of models dealing with biomass allocation exist, we lack a synthetic understanding of the underlying processes. This is partly due to the lack of suitable datasets for validating and parameterising models. To that end, we present the Biomass And Allometry Database (BAAD) for woody plants. The BAAD contains `r sum(!is.na(data[,vars]))` measurements collected in `r length(unique(data$studyName))` different studies, from `r nrow(data)` individuals across `r length(unique(data$species))` species. Most of these data come from an existing publication, however, raw data were rarely made public at time of publication. Thus the BAAD contains individual level data from different studies, transformed into standard units and variable names. The transformations were achieved using a common workflow for all raw data files. Other features which distinguish the BAAD are: i) measurements were for individual plants rather than stand averages; ii) individuals spanning a range of sizes were measured; iii) inclusion of plants from 0.01-100m in height; and iii) biomass was estimated directly, i.e. not indirectly via allometric equations (except in very large trees where biomass was estimated from detailed sub-sampling). We included both wild and artificially grown plants. The dataset contains the following size metrics: total leaf area; area of stem cross-section, including sapwood, heartwood, and bark; height of plant and crown base, crown area and surface area; and the dry mass of leaf, stem, branches, sapwood, heartwood, bark, coarse roots and fine root tissues. We also report other properties of individuals (age, leaf size, leaf mass per area, wood density, nitrogen content of leaves and wood), as well as information about the growing environment (location, light, experimental treatment, vegetation type) where available. It is our hope that making these data available will improve our ability to understand plant growth, ecosystem dynamics, and carbon cycling in the world's vegetation.
